%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Remi Marchand}
\address{1 Gormley Court \linebreak Richmond Hill, ON}
\contacts{647-995-3645 \linebreak hireme@remimstr.com}

\begin{document}

	% Print the header
	\makeheader

	\begin{cvsection}{Profile}
		\vspace{2pt}
		\begin{cvsubsection}{}{}{}
			I am an energetic software developer with a passion for best practices and writing high quality, scalable code.
			In my 3+ years of software development, I have designed, built, tested, and maintained complex front-end codebases;
			improved everything from code to product management practices to onboarding docs, and scrum processes;
			and managed small teams of developers and interns. I am not afraid to voice my opinions, back them up with evidence,
			and put in the elbow grease needed to change things for the better!
		\end{cvsubsection}
	\end{cvsection}

	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Dev \& Scrum Master}{Gubagoo}{Dec 2020 - Present}
 			\begin{itemize}
				\item Overhauled my team's scrum development process resulting in better estimations, alignment, and deliveries.
				\item Took initiative to fix over 1200 eslint errors that were preventing us from enforcing a consistent coding style.
				\item Advocated for integration testing. Set up Cypress to run tests against every pull request using Github Actions.
				\item \textbf{Technologies:} React, Redux, Cypress, Emotion, Storybook, SocketIO
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Software Developer}{Walmart Labs}{Oct 2020 -- Dec 2020 - Layoff}
			\begin{itemize}
				\item Implemented style linting to improve CSS consistency and encourage the usage of global styles.
				\item Participated in daily standups, grooming, planning, and more. Wrote JIRA tickets for technical tasks.
				\item \textbf{Technologies:} React, Redux, TypeScript, Jest, Enzyme, Emotion, Storybook
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Software Developer \& Designer}{Acerta}{July 2018 -- Oct 2020}
			\begin{itemize}
				\item Designed and developed key product features, including a "module"-based design that improved scalability.
				\item Developed over 10 Demo UIs for sales reps to show to clients during pitches.
				\item Leveraged leadership skills to lead a company-wide hackathon to foster a culture of learning and collaboration.
				\item Mentored co-op students by guiding them through tasks, allowing them reach their full potential as contributors.
				\item \textbf{Technologies:} React, Redux, TypeScript, Jest, Styled-Components, AntD, Echarts, Docker, Azure, Moqups
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Full-Stack Developer Intern}{Ontario Institute for Cancer Research}{Winter \& Spring 2017}
			\begin{itemize}
				\item Helped the project gain funding by adding features such as new page designs and search functionality.
				\item Reduced deployment effort using technologies such as docker-compose and webpack.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Waterloo, ON}{University of Waterloo}{Fall 2013 -- May 2018}
			\begin{itemize}
				\item B.Sc. in Biology with Minor in Computer Science.
				\item Coursework: C/C++/Python; Databases; Algorithms; Networking; Bioinformatics Algorithms.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{COVID-19 Globeview} (2020). Developed a tool for visualizing the spread of COVID-19 on a globe broken down by region and time.
					https://covid19globe.remimstr.com (Vanilla.js, Echarts)
				\item \textbf{Personal Website} (2020). Portfolio site for showing off my work: https://remimstr.com (Svelte)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{Languages:} JavaScript, TypeScript, CSS, Python, SQL, C (prior experience), C++ (prior experience)
				\item \textbf{Frameworks \& Libraries:} React, Redux, Svelte, AngularJS, Styled-Components, TailwindCSS, OpenAPI
				\item \textbf{Tools:} Docker, Docker-Compose, Linux, Microsoft Azure, Node.js, Webpack, Jest, Mocha/Chai, Selenium, Cypress, Nginx, MongoDB (prior experience), Elasticsearch (prior experience)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

\end{document}
